PEACE: {\underline P}arallel {\underline E}nvironment for {\underline A}ssembly and {\underline C}lustering of Gene {\underline E}xpression

### 2010-04-20 papers/NAR_web_server_2009/paper.sup.tex
Modifications to reviewer response

\sloppy 
\usepackage{graphicx}
\bibliographystyle{natbib}

% Using the following to mark changes for review
\usepackage{color}
\definecolor{blue}{rgb}{0,0,1}
\newcommand{\mc}[1]{\textcolor{blue}{#1}}
%\newcommand{\mc}[1]{#1}   % Replace above line with this to eliminate all coloring

@@

\subsection{Adaptive $d^2$}

In the above discussion of $d^2$ we assume sequences of at least 100 bp, and
in pratice use a window of size 100.  While the technique should be,
in principle, adaptable to short-read sequences (decreasing window
size as necessary), there are some problems in the details.
Diminishing window sizes implies both diminishing accuracy (requiring
the thrshold be adjusted) and increasing runtime (as there are
potenitally more window pairs).  More importantly, there is the
problem of non-homogonous sequence lengths: short-read technologies
tend to produce short reads, but can still include quite long reads in
their output.  Hence it is not immediately clear how to compare a very
short read against a very long one.

We address these issues with our {\it adaptive $d^2$} strategy that
works as follows: we put sequences, based on length, into three {\it
  overlapping} groups (i.e. sequences less than length XXX, sequences
between length YYY and ZZZ, and seqeunces greater than AAA).  For each
group we pick a constant windowsize and threshold tailored to the
length range of the group (as well as filtering heurstic constants),
and use those values when computing the $d^2$ distance for two
sequences in the same group.  We do not compute distances between
sequences in different groups. Once computed, we assign to the MST
edge the ratio of the $d^2$ score to the group threshold, thus
normalizing the weight for comparisons ``between groups'' and
effectivally giving us an edge-removal threhold of 1.

By restricting $d^2$ comparisons to within a group, we minimize the
effets of the hetrogenous sequences lengths by restricting our
comparisons to only sequences of similar lengths.  By not restrcicting
ourselves to a single window size, we allow ourselves to, when possible, avoid the
preformance hit of using a small window.  As we are not comparing
sequences from different groups we bypass the question of how to
compare a largelong sequence against a short one.  And because the
groups overlap in content, we still get implicit comparisons between
long and short sequences in terms of the resulting path of the minimum
spanning tree that makes use of these ``linking'' nodes.

In the \textsc{peace} implementation, we subdevide into three groups:
NEED INFO.

@@

\mc{ Our primary measurement tools if mesurement are sensitivity, the
Jaccard Index, Type 1 error and Type 2 error
(Figure~\ref{sensitivityFig}).  Sensitivity is the ratio for true
positives to actual positives ($tp / (tp + fn)$) -- the fraction of
sequences from the same transcript that are identified as such.  The
{\it Jaccard} index combines both sensitivity and specificity,
calculated as the ratio of true positives to the sum of true
positives, true negatives, and false positives ($tp / (tp+fn+fp)$)
[\cite{Hazelhurst08a}].  Notably, when we removed duplicated genes
before generating the simulated EST sets, we found all three tools to
have 100\% specificity: no false positives. }

\mc{Type 1 and Type 2 errors, as defined in {\it Wang et al.}
[\cite{Wang04}], measure quality at the level of the genes from which
the ESTs were derived.  For Type 1 error, we look at the fraction of genes
that were broken into two or more partitions, while in
Type 2 error we look at the fraction of clusters that contain two or
more genes.   }

\mc{A fifth metric is to look at the number of singletons produce by a
  tool:  sequences that  could not  be  assigned to  any cluster.   In
  practice such a sequence could represent compelte coverage of a very
  short transcript (one that may be otherwise had to identify), but is
  more likely to be an error in the clustering algorithm.  In order to
  identify  the first  it is  important  to minimize  the second.   In
  Figure~\ref{singletons} we look at the number of singletons produced
  by each tool when run on  simulated data in which there should be no
  singletons produced,  seeing a very slight improvment  of PEACE over
  WCD in certain error ranges.}

\begin{figure}[tbp]
\centerline{
\label{dups}
\includegraphics[scale=0.35]{pics.d/singletons_40.pdf}
}
\caption{Number of singletons produced by each tool in a simulated run
  where a fully correct clustering would have no singletons.  Values
  average over 30 triles.  Blue/Solid = \textsc{peace}, Green/Dashed =
  \textsc{wcd}, Black/Dot-Dashed = \textsc{cap3}.}\label{singletons}
\end{figure}

@@

In Figure~\ref{dups} we look at the ability of each tool to separate
duplicates as a function of the \% divergence between the
duplications.  Unsurprisingly, \textsc{cap3} (the assembler) does the best
here, able to effectively separate duplicates at $~92\%$ similarity
or less.  \textsc{peace} and \textsc{wcd} are roughly comparable, both clearly able to
separate duplicates out at a similarity level of $83\%$ -- but completely 
unable to distinguish sharing a similarity of $~88\%$ or more.

\begin{figure}[tbp]
\centerline{
\label{dups}
\includegraphics[scale=0.35]{pics.d/duplicates_40.pdf}
}
\caption{Ability to distinguish duplicates as a function of
  divergence.  Estimates averaged over 30 trials; one trial consists
  of taking a random gene, copying it and stochastically changing bases
  at the specified rate, then using the two genes as the bases for
  generating a simulated set. Blue/Solid = \textsc{peace}, Green/Dashed = \textsc{wcd}, Black/Dot-Dashed = \textsc{cap3};
  variance was too small for visible plotting of
  confidence intervals.}
\end{figure}

\subsection{Raising the Threshold}
\mc{ 
  The \wcd\/ tool uses a $d^2$ threshold of $40$ to determine whether
  two sequences are in the same cluster.  As this is equivilent to our
  $T$ threshold for dismissing MST edges, we have set it to the same
  default value when used for Sanger sequences.  However, we did
  experiment with higher values, to interesting results.  A basic
  analysis indicated that a $T$ value as high as 130 should not have a
  significant impact on its effectivness as a descriminator.  And in
  fact this was born out in simulation, as shown in
  Figure~\label{SiJiT1T2130}.  In contrast with the equivilent results
  for a threshold of $T=40$, as shown in the manuscript, we see
  considerable improvement in \peace\/ over \wcd\/ in all metrics
  except Type 2 error, in which \wcd\/ slightly
  better. Unsurprisingly, this also makes a significant difference in
  the tool's ability to distinguish duplications: we see fairly poor
  performance in Figure~\ref{dups130}.  
}

\mc{
  Most importantly, while the higher threshold appeared to be better
  in theory and in analysis, it did not hold in practice.  In
  Table~\ref{SangerTable130} we show the match to the manuscript
  Table~\ref{SangerTable}, and observe the poor performance of
  \peace\/ when looking at the Jaccard index.  It is clear that in the
  real data, the level of similarity is consierably higher then in the
  simulations, thus making the reduced specificity of the higher
  threshold considerably more of a problem.
XXX}

\begin{figure}
  \centerline{\includegraphics[width=3.35in]{pics.d/SeJiT1T2x40.pdf}}
  \caption{Comparisons of Sensitivity, Jiccard Index, Type 1 error and
    Type 1 error, based on the
    average over 30 simulated Sanger Sequence ESTs sets derived from 100 zebra
    fish genes  (see
    Supplementary Materials, Section C, for more details).  Blue/Solid
    = \peace, Green/Dash = \wcd, Black/Dot-Dash = \capthree; vertical
    tics = 95\% confidence intervals on estimates.  Intervals are not
    presented for Type 1 error due to the effective lack of
    variance.}\label{SeJiT1T2130}
\end{figure}

\begin{figure}[tbp]
\centerline{
\label{dups130}
\includegraphics[scale=0.35]{pics.d/duplicates_130.pdf}
}
\caption{Ability to distinguish duplicates as a function of
  divergence.  Estimates averaged over 30 trials; one trial consists
  of taking a random gene, copying it and stochastically changing bases
  at the specified rate, then using the two genes as the bases for
  generating a simulated set. Blue/Solid = \textsc{peace}, Green/Dashed = \textsc{wcd}, Black/Dot-Dashed = \textsc{cap3};
  variance was too small for visible plotting of
  confidence intervals.}
\end{figure}

\subsection{Runtime}
\label{rt_section}

In Figure~\ref{seq_runtime} we see give a runtime comparison of \textsc{peace} and \textsc{wcd},
seeing a slight improvement in \textsc{peace}.  (As \textsc{cap3} performs both
clustering and assembly, runtime comparisons are not meaningful.)  As
stated, we see an almost perfectly quadratic curve ($r > 0.99$),
indicating that the runtime is dominated by the time required to look
at every EST pair (either filtering or computing $d^2$).
As both \textsc{peace} and \textsc{wcd} can be run in a parallel mode, we also
examined runtime as a function of the ratio of EST set sizes to number
of processors used.  In Figure~\ref{par_runtime} we show two such ratios,
again seeing an improvement in \textsc{peace} over \textsc{wcd}.

\mc{All tests were run on the University of Miami Redhawk cluster,
  made up of 3.2 GHz Intel Xeon EM64T CPUs, each with a 2MB cache and
  800 MHz side bus, model number Xeon LV 3.0 (2005).}

%%%%%%%%%%%%%
\begin{figure}[tbp]
\centerline{
\includegraphics[scale=0.35]{pics.d/seq_time.pdf}
\label{seq_runtime}
}
\caption{Single Processor Runtime as a function of input size,
  averaged over 50 simulated EST sets; Blue/Solid = \textsc{peace},
  Green/Dashed = \textsc{wcd}; vertical tics represent= 95\% confidence
  intervals on estimates.}
\end{figure}
\begin{figure}[tbp]
\centerline{
\includegraphics[scale=0.5]{pics.d/par_time.pdf}
\label{par_runtime}
}
\caption{Runtime of a function of input size when holding constant the
  ratio of set size to number of processors used; averaged over 30
  simulated EST sets.  Blue/Solid = \textsc{peace}, Green/Dashed = \textsc{wcd};
  vertical tics represent= 95\% confidence intervals on estimates.}
\end{figure}
%%%%%%%%%%%%%

\section{Raising the Threshold Real Data Sets}

\begin{table}[tbp]
\begin{center}
\begin{tabular} {| c || c || c | c | c | c | c | c | c |}
\hline
 & 
& Sensitivity & Jaccard & \begin{tabular}{c} Type 1 \\
  error \end{tabular} & \begin{tabular}{c} Type 2 \\
  error \end{tabular} &
\begin{tabular}{c} Number \\ of  \\
    Clusters \end{tabular} & \begin{tabular}{c} Number \\ of \\
    Singletons \end{tabular}
    & \begin{tabular}{c} Single \\ processor \\ runtime (s) \end{tabular} \\
\hline EasyCluster Human & \peace & 0.999 & 0.106 & 0.027 & 0.030 & 67 & 2 & 295 \\
\cline{2-9} Benchmark & \wcd & 0.998 & 0.672 & 0.144 & 0.044 & 113 & 16 & 804 \\
\cline{2-9} (111 Genes) & \capthree & 0.657 & 0.643 & 1 & 0.001 & 2269 & 1827 & \mbox{NA} \\
\hline
\hline WCD A076941 & \peace & 0.937 & 0.345 & 0.337 & 0.0342 & 18256 & 8135 & 1293 \\
\cline{2-9} Benchmark & \wcd & 0.933 & 0.476 & 0.350 &  0.027 & 18787 & 8553 & 966 \\
\cline{2-9} (13240 genes) & \capthree & 0.826 & 0.802 & 0.486 & 0.014 & 25042 & 14916 &
\mbox{NA} \\
\hline
\end{tabular}
\label{SangerReal130}
\end{center}
\caption{Comparisons of runs on the EasyCluster human Benchmark
  Dataset and the WCD A076941 Arabidopsis thaliana dataset using the
  standard quality measurments with $T=130$.}
\end{table}

@@

% LocalWords:  overline TpG li lj lk ijk i'j'k jj kk trinucleotides rb Arndt et
% LocalWords:  transversion Arndt's dinucleotides transversions RepBase arallel
% LocalWords:  nalysis lustering ngine al substring Hazelhurst \textsc{wcd}  ESTsim ESTs
% LocalWords:  polymearse Methodoloy Jaccard tp fn fp  wcd th Prim's Ns
% LocalWords:  Chlamydomonas reinhartdii

>>>>

\usepackage[pdftex,
colorlinks=true, %makes the links show up in color, rather than in a box
citecolor=black, %color of the in-text citation numbers
urlcolor=blue %color of the url links
]{hyperref}
\usepackage{wrapfig}
\bibliographystyle{unsrt}

%\usepackage[pdftex,
%colorlinks=true, %makes the links show up in color, rather than in a box
%citecolor=black, %color of the in-text citation numbers
%urlcolor=blue %color of the url links
%]{hyperref}

\sloppy 
\usepackage{graphicx}
%\bibliographystyle{natbib}

% Using the following to mark changes for review
\usepackage{color}
\definecolor{red}{rgb}{1,0,0}
\newcommand{\mc}[1]{\textcolor{red}{#1}}
%\newcommand{\mc}[1]{#1}   % Replace above line with this to eliminate all coloring

@@

\section{Adaptive $d^2$}

\mc{In the above discussion of $d^2$ we assume sequences of at least 100
bp, and in practice use a window of size 100.  While the technique
should be, in principle, adaptable to short-read sequences (decreasing
window size as necessary), there are some problems in the details.
Diminishing window sizes implies both diminishing accuracy (requiring
the threshold be adjusted) and increasing runtime (as there are
potentially more window pairs).  More importantly, there is the
problem of non-homogeneous sequence lengths: short-read technologies
tend to produce short reads, but some technologies can still include
long reads in their output.  Hence it is not immediately clear how to
compare a very short read against a very long one.}

\mc{We address these issues with our {\it adaptive $d^2$} strategy that
works as follows: we partition sequences by length into disjoint groups.  For each
group we pick a constant window size and threshold tailored to the
length range of the group (as well as filtering heuristic constants),
and use those values when computing the $d^2$ distance for two
sequences in the same group.  We do not compute distances between
sequences in non-adjacent groups (i.e. a member of the ``shortest
groups'' against a member of the ``longest groups'' if there is an
intervening sized group).  Once computed, we assign to the MST
edge the ratio of the $d^2$ score to the group threshold, thus
normalizing the weight for comparisons ``between groups'' and
effectively giving us an edge-removal threshold of 1.}

\mc{By restricting $d^2$ comparisons to within a group, we minimize the
effects of the heterogeneous sequences lengths by restricting our
comparisons to only sequences of similar lengths.  By not restricting
ourselves to a single window size, we allow ourselves to, when possible, avoid the
performance hit of using a small window.  As we are not comparing
sequences from different groups we bypass the question of how to
compare a long sequence against a short one.  And because the
groups overlap in content, we still get implicit comparisons between
long and short sequences in terms of the resulting path of the minimum
spanning tree that makes use of these ``linking'' nodes.}

\mc{In the \textsc{peace} implementation, we subdivide into three groups:
\begin{itemize}
\item Less than 150 ($w=50$, $T=40$, $t=20$, $u=4$).
\item Between 150 and 400 ($w=75$, $T=60$, $t=35$, $u=6$)
\item Greater than 400 ($w=100$, $T=80$, $t=50$, $t=50$).
\end{itemize}}

@@

\mc{Our primary measurement tools if measurement are sensitivity, the
Jaccard Index, Type 1 error and Type 2 error
(Figure~3).  Sensitivity is the ratio for true
positives to actual positives ($tp / (tp + fn)$) -- the fraction of
sequences from the same transcript that are identified as such.  The
{\it Jaccard} index combines both sensitivity and specificity,
calculated as the ratio of true positives to the sum of true
positives, true negatives, and false positives ($tp / (tp+fn+fp)$)
\cite{Hazelhurst08a}.  Notably, when we removed duplicated genes
before generating the simulated EST sets, we found all three tools to
have perfect specificity: no false positives.}

\mc{Type 1 and Type 2 errors, as defined in {\it Wang et al.}
\cite{Wang04}, measure quality at the level of the genes from which
the ESTs were derived.  For Type 1 error, we look at the fraction of genes
that were broken into two or more partitions, while in
Type 2 error we look at the fraction of clusters that contain two or
more genes.}

\mc{A fifth metric is the number of singletons produce by a
  tool:  sequences that  could not  be  assigned to  any cluster.   In
  practice such a sequence could represent complete coverage of a very
  short transcript (one that may be otherwise had to identify), but is
  more likely to be an error in the clustering algorithm.  In order to
  identify  the first  it is  important  to minimize  the second.   In
  Figure~\ref{singletons} we look at the number of singletons produced
  by each tool when run on  simulated data in which there should be no
  singletons produced,  seeing a very slight improvement  of PEACE over
  WCD in certain error ranges.}

\begin{figure}[tbp]
\centerline{
\includegraphics[scale=0.35]{pics.d/singletons_40.pdf}
}
\caption{Number of singletons produced by each tool in a simulated run
  where a fully correct clustering would have no singletons.  Values
  average over 30 trials.  Blue/Solid = \textsc{peace}, Green/Dashed =
  \textsc{wcd}, Black/Dot-Dashed = \textsc{cap3}.}\label{singletons}
\end{figure}

@@

In Figure~\ref{dups} we look at the ability of each tool to separate
duplicates as a function of the \% divergence between the
duplications.  Unsurprisingly, \textsc{cap3} (the assembler) does the best
here, able to effectively separate duplicates at $~92\%$ similarity
or less.  \textsc{peace} and \textsc{wcd} are roughly comparable, both clearly able to
separate duplicates out at a similarity level of $78\%$ -- but completely 
unable to distinguish sharing a similarity of $~88\%$ or more.

\begin{figure}[tbp]
\centerline{
\includegraphics[scale=0.35]{pics.d/duplicates_40.pdf}
}
\caption{Ability to distinguish duplicates as a function of
  divergence.  Estimates averaged over 30 trials; one trial consists
  of taking a random gene zebra-fish gene, copying it and stochastically changing
  bases at the specified rate, then using the two genes as the bases
  for generating a simulated set. Blue/Solid = \peace, Green/Dashed =
  \wcd\/ (mostly obscured by the blue line), Black/Dot-Dashed =
  \capthree; variance was too small for visible plotting of
  confidence intervals.}\label{dups}
\end{figure}

\subsection{Raising the Threshold}
\label{sim_thresh}
\mc{ 
  The \wcd\/ tool uses a $d^2$ threshold of $40$ to determine whether
  two sequences are in the same cluster.  As this is equivalent to our
  $T$ threshold for dismissing MST edges, we have set it to the same
  default value when used for Sanger sequences.  However, we did
  experiment with higher values, to interesting results.  A basic
  analysis indicated that a $T$ value as high as 130 should not have a
  significant impact on its effectiveness as a discriminator.  And in
  fact this was born out in simulation, as shown in
  Figure~\label{SiJiT1T2130}.  In contrast with the equivalent results
  for a threshold of $T=40$, as shown in the manuscript, we see
  considerable improvement in \peace\/ over \wcd\/ in all metrics
  except Type 2 error, in which \wcd\/ slightly
  better. Unsurprisingly, this also makes a significant difference in
  the tool's ability to distinguish duplications: we see fairly poor
  performance in Figure~\ref{dups130}.  
}

\mc{
  Most importantly, while the higher threshold appeared to be better
  in theory and in analysis, it did not hold in practice.  In
  Table~\ref{SangerReal130} we show the match to the manuscript
  Table~1, and observe the poor performance of
  \peace\/ when looking at the Jaccard index.  It is clear that in the
  real data, the level of similarity is considerably higher then in the
  simulations, thus making the reduced specificity of the higher
  threshold considerably more of a problem.
}

\begin{figure}
  \centerline{\includegraphics[width=3.35in]{pics.d/SeJiT1T2x40.pdf}}
  \caption{Comparisons of Sensitivity, Jaccard Index, Type 1 error and
    Type 1 error, based on the
    average over 30 simulated Sanger Sequence ESTs sets derived from 100 zebra
    fish genes  (see
    Supplementary Materials, Section C, for more details).  Blue/Solid
    = \peace, Green/Dash = \wcd, Black/Dot-Dash = \capthree; vertical
    tics = 95\% confidence intervals on estimates.  Intervals are not
    presented for Type 1 error due to the effective lack of
    variance.}\label{SeJiT1T2130}
\end{figure}

\begin{figure}[tbp]
\centerline{
\includegraphics[scale=0.35]{pics.d/duplicates_130.pdf}
}
\caption{Ability to distinguish duplicates as a function of
  divergence.  Estimates averaged over 30 trials; one trial consists
  of taking a random zebra-fish gene, copying it and stochastically changing bases
  at the specified rate, then using the two genes as the bases for
  generating a simulated set. Blue/Solid = \textsc{peace}, Green/Dashed = \textsc{wcd}, Black/Dot-Dashed = \textsc{cap3};
  variance was too small for visible plotting of
  confidence intervals.}\label{dups130}
\end{figure}

\section{Real Data}

\subsection{Runtimes}

In Table~\ref{RunTime} we show the runtime of \peace\/ and \wcd\/ on
five different benchmark sets obtained from the WCD and EasyCluster
studies \cite{Hazelhurst08a,Picardi09}.

\begin{table}[tbp]
\begin{center}
\begin{tabular} {|c|| c | c || c | c |}
\hline
 Benchmark & \begin{tabular}{c} Number of \\ Sequences \end{tabular}
 & \begin{tabular}{c} Number of \\ Bases \end{tabular} & Peace Runtme (s)&
 WCD Runtime (s) \\
\hline
\hline
 Human Cluster & 17733 & 11.7 Mb & 293 & 804 \\
\hline
 Cotton & 29,995 & 17.1 Mb & 222 & 339 \\
\hline
 Ricinus & 57,690 & 40.9 Mb & 1344 & 2356 \\
\hline
 A076941 & 76,941 & 32.8 Mb & 1166 & 966 \\
\hline
\hline
 A686903 & 686,904 & 294.7 Mb & 9449 & 2481 \\
\hline
\end{tabular}
\end{center}
\caption{Runtime for \peace\/ and \wcd\/ on benchmarks from the
  WCD and EasyCluster studies \cite{Hazelhurst08a, Picardi09}.
  Runtimes for the first four sets are sequential, while that last was
  run over thirty processors.}\label{RunTime}
\end{table}

\subsection{Higher Threshold}

\mc{ In Table~\ref{SangerReal130} we see the effect on the application
  of \peace\/ to the data sets from Table~1 when
  raising the threshold $T$ to 130 (see previous discussion in
  Section~\ref{sim_thresh}).  While doing this appeared to be fairly
  effective in simulation, it did not hold up in practice.  We see
  essentially no change in the sensitivity, but significant changes in
  the Jaccard Index (and a corresponding decrease in the total number
  of clusters).  We suspect that this is due to a higher number of
  more closely related genes than are present in the simulated
  data. Regardless, without considerably more investigation, these
  results indicated we should be leaving $T$ at a default rate of 40.
}

\begin{table}[tbp]
\begin{center}
\begin{tiny}
\begin{tabular} {| c || c || c | c | c | c | c | c | c |}
\hline
 & 
& Sensitivity & Jaccard & \begin{tabular}{c} Type 1 \\
  error \end{tabular} & \begin{tabular}{c} Type 2 \\
  error \end{tabular} &
\begin{tabular}{c} Number \\ of  \\
    Clusters \end{tabular} & \begin{tabular}{c} Number \\ of \\
    Singletons \end{tabular}
    & \begin{tabular}{c} Single \\ processor \\ runtime
      (s) \end{tabular} \\
\hline
\hline EasyCluster Human & PEACE & 0.999 & 0.106 & 0.027 & 0.030 & 67 & 2 & 295 \\
\cline{2-9} Benchmark & WCD & 0.998 & 0.672 & 0.144 & 0.044 & 113 & 16 & 804 \\
\cline{2-9} (111 Genes) & Cap3 & 0.657 & 0.643 & 1.000 & 0.001 & 2269 & 1827 & \mbox{NA} \\
\hline
\hline WCD A076941 & PEACE & 0.937 & 0.345 & 0.337 & 0.0342 & 18256 & 8135 & 1293 \\
\cline{2-9} Benchmark & WCD & 0.933 & 0.476 & 0.350 &  0.027 & 18787 & 8553 & 966 \\
\cline{2-9} (13240 genes) & Cap3 & 0.826 & 0.802 & 0.486 & 0.014 & 25042 & 14916 &
\mbox{NA} \\
\hline
\end{tabular}
\end{tiny}
\end{center}
\caption{Comparisons of runs on the EasyCluster human Benchmark
  Dataset and the WCD A076941 Arabidopsis thaliana dataset using the
  standard quality measurements with $T=130$.}\label{SangerReal130}

\end{table}

@@

% LocalWords:  overline TpG li lj lk ijk i'j'k jj kk trinucleotides rb Arndt et
% LocalWords:  transversion Arndt's dinucleotides transversions RepBase arallel
% LocalWords:  nalysis lustering ngine al substring Hazelhurst \textsc{wcd}  ESTsim ESTs
% LocalWords:  polymearse Methodoloy Jaccard tp fn fp  wcd th Prim's Ns ssembly
% LocalWords:  Chlamydomonas reinhartdii nvironment xpression runtime bp Runtme
% LocalWords:  stochastically Runtimes EasyCluster Ricinus Dataset
